{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking

### 2013-10-04 paper/paper.tex
start of intro

>>>>

Program synthesis is the mechanized construction of software that provably
satisfies a given specification.  Synthesis tools promise to relieve the
programmer from thinking about \emph{how} the problem is to be solved;
instead, the programmer only provides a compact description of \emph{what}
is to be achieved.  Foundational research in this area has been
exceptionally fruitful, beginning with Alonso Church's work on the
\emph{Circuit Synthesis Problem} in the sixties.  In this paper, we present
a new method that brings the promise of automating programming closer to
application.
